\section{Introduction}
This document is a quick guide for users who want to generate CRTM MW instrument coefficients (\emph{TauCoeff} and \emph{SpcCoeff} files) as part of the CRTM Transmittance Coefficient Generation Package v1.0 (henceforth called TCGP) tutorial. 
A minimal set of instructions is provided to achieve this goal. This tutorial is written for the \emph{bash} terminal.

\section{Preliminaries}
Using the TCGP v1.0 requires setting up its environment. The TCGP makes use of CRTM modules and thus cannot run without a working installation of the CRTM v2.4.0+. Likewise the build environment of the TCGP code itself needs to be set beforehand.

\subsection{Requirements}
Building CRTM and TCGP requires the following dependencies:
\begin{itemize}
  \item HDF5 and netCDF4.
  \item A shared-memory multiprocessing API, such as OpenMP.
\end{itemize}

\subsection{Building the CRTM}
In this section a minimal approach towards compiling the CRTM using the ecbuild build system is provided. 
The ecbuild system from the ECMWF needs to be cloned and added to the \verb|PATH|:
\begin{verbatim}
git clone https://github.com/ecmwf/ecbuild
export PATH=$PWD/ecbuild/bin:$PATH
\end{verbatim}
The CRTM repository needs to be cloned and the CRTM environment needs to be set:
\begin{verbatim}
git clone https://github.com/JCSDA-internal/crtm
cd crtm
. ./Set_CRTM_Environment.sh
\end{verbatim}
Building the CRTM is straightforward at this point:
\begin{verbatim}
mkdir build
cd build/
ecbuild ..
make 
\end{verbatim}
This process may take a few minutes to complete, depending on your system.
Lastly, the successful build of the CRTM can tested by simply typing:
\begin{verbatim}
ctest
\end{verbatim}

\subsection{Setting make.macros for the TCGP}
The first step to build the TCGP applications is to select the \verb|make.macros| file appropriate for your machine.
Currently, the following systems are actively supported:
\begin{itemize}
  \item macOS homebrew
  \item GNU Linux
  \item SSEC S4
  \item NCCS Discover
  \item MSU Orion
\end{itemize}

Using the TGCP on S4 as an example would then require using the appropriate \verb|make.macros| file:
\begin{verbatim}
cd CRTM_coef
rm make.macros
ln -s make.macros.s4 make.macros 
\end{verbatim}
This completes the setup of the TCGP.